Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-05 manuscript.Rmd
Uncited working.

# If HD article count is missing, replace with Scopus count
df.96.10$HD.N <- ifelse(is.na(df.96.10$HD.N), df.96.10$scopus.N, df.96.10$HD.N)

# Some counts have 0 values.  Set these to NA and then omit
df.96.10$HD.N <-ifelse(df.96.10$HD.N == 0, NA, df.96.10$HD.N) 
df.96.10 <- df.96.10[!is.na(df.96.10$HD.N), ]

@@

# If uncited proportion is missing because it was not in scopus, replace the missing
# value with the overall mean uncited proportion

@@

uncited.df <- rbind(df.96.10.Summary, df.95.11) %>%
    arrange(Year)
uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100    
uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited")], id.vars = "Year")

@@

ggplot(observed.df.melted, aes(Year, value, colour = variable)) + 
    geom_line(alpha = .60) + 
    geom_point(size =4) +
    scale_color_manual(values=cp, labels = c("Number of Articles Published",
         "Estimated Number of Uncited Articles")) +
    theme(legend.title=element_blank()) +
    theme(legend.position = "bottom") +
    ylab("N") +
    geom_text(data = percent.df, aes(Year, Uncited -70, label = percentLabel), size =4, colour = "black") +
    scale_y_continuous(breaks = seq(0, 2250, 250), limits = c(0, 2250))

>>>>

# If HD article count is missing, replace with Scopus count

# Some counts have 0 values.  Set these to NA and then omit.
df.96.10$HD.N <-ifelse(df.96.10$HD.N == 0, NA, df.96.10$HD.N) 
df.96.10 <- df.96.10[!is.na(df.96.10$HD.N), ]

@@

# If uncited proportion is missing because it was not in Scopus, replace the missing
# value with the overall mean uncited proportion

@@

uncited.df <- rbind(df.96.10.Summary, df.95.11) %>%
    arrange(Year)
uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100

uncited.df <- left_join(uncited.df, journals.year, by = "Year")

uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited", "N.Journals")], id.vars = c("Year", "N.Journals"))

@@

ggplot(uncited.melted, aes(Year, value, colour = variable,)) + 
    geom_line(alpha = .60) + 
    geom_point(size = 4) +
    scale_color_manual(values=cp, labels = c("Number of Articles Published",
         "Estimated Number of Uncited Articles")) +
    theme(legend.title=element_blank()) +
    theme(legend.position = "bottom") +
    ylab("N") +
    geom_text(data = percent.df, aes(Year, Uncited -70, label = percentLabel), size =4, colour = "black") +
    scale_y_continuous(breaks = seq(0, 2250, 250), limits = c(0, 2250))
